sensiAnPaper1All

### 2015-07-21 sensiAnPaper1All.Rmd
add an extra predictor (ratio of P_1 and P_2)

```{r}
  library(resistance)

@@

  rowSums(resistBetterMix1Seq)/ncol(resistBetterMix1Seq)
  #100runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #                .25                   .26                   .30   
  #1000runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #               .178                  .232                  .238

@@

  rowSums(resistBetterMix2Seq)/ncol(resistBetterMix2Seq)  
  #1000runs
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #             0.471                0.568                0.551

@@

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix3Seq)/ncol(resistBetterMix3Seq)
  #100runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                  .83                   .75                   .72 
  #1000runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                .794                  .726                  .673

@@

  #hardcode which variables to include in the tree analysis here
  #to keep it simple and transparent
  treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  treeInput <- treeInput[ treePredictors, ]

>>>>

```{r}

  #library(devtools)
  #install_github('AndySouth/resistance')
  library(resistance)

@@

  rowSums(resistBetterMix1Seq)/ncol(resistBetterMix1Seq)
  #100runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #                .25                   .26                   .30   
  #1000runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #               .178                  .232                  .238 
  #new100
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #              0.18                 0.24                 0.25

@@

  rowSums(resistBetterMix2Seq)/ncol(resistBetterMix2Seq)  
  #1000runs
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #             0.471                0.568                0.551 
  #new100
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #              0.58                 0.57                 0.52

@@

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix3Seq)/ncol(resistBetterMix3Seq)
  #100runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                  .83                   .75                   .72 
  #1000runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                .794                  .726                  .673  
  #new100
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #              0.83                 0.79                 0.72

@@

  #add an extra predictor, the lower starting freq of resistance divided by the larger
  startResistanceRatio <- ifelse( treeInput['P_1',] < treeInput['P_2',], treeInput['P_1',]/treeInput['P_2',], treeInput['P_2',]/treeInput['P_1',])
  treeInput <- rbind(treeInput,startResistanceRatio)

  #hardcode which variables to include in the tree analysis here
  #to keep it simple and transparent
  treePredictors <- c('P_1','P_2','startResistanceRatio','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  treeInput <- treeInput[ treePredictors, ]
